\documentclass[11px]{article}

\usepackage[a4paper, total={7in, 9.3in},top=20mm,bottom=10mm]{geometry}


\begin{document}
	\begin{center}
	\section*{Obaro I. Johnson}
	Email: johnson.obaro@hotmail.com
	
    Phone: $+$44(0)7423004067
    \end{center}
    %Horizontal line
   \makebox[\linewidth]{\rule{\paperwidth}{0.1pt}}
	
	\subsection*{Profile}
	I graduated from the department of computer science at University of West London, UK. Graduated with first class degree with previous industrial experience as a software engineer in   Iris software  (a payroll company, UK),Tripleplay-Services(IPTV software company) and also have worked as a computer instructor. I'm a quick learner and keen to learn new skills with the ability to work in a challenging environment.  I am currently working for Johnson Control - Tyco Fire Panel as a Window Software Engineer.
	
\section*{Skills}
 \begin{itemize}
 	\item JavaScript, HTML, CSS,PHP, NodeJs, JQuery, ReactJs, NodeJS developer for Web Development.
 	 
 	\item  C\#,  C/C$++$, Java, for window base application development.
 	\item Knowledge on QT GUI,Window's MFC Framework, WPF.
 	
 	\item Web Services, RestFul API developer.
 	   
 	\item Design Pattern
 	     Strong Knowledge on OOP and SOLID Principle, 	     
 	     Test Driven Development.
 	\item Others 	
 	  - Advance Knowledge in Mathematics. 	  
 	  - Knowledge on Graphical Hardware programming. 	  
 	  - Problem solving skills, 	  
 	  - Knowlege on SQL and Mysql database for application development
 	  
 	  - Relational Database Modelling/Uniform Modelling Language(UML),
 	 
 	  - Embedded System Programming 
 	 
	 	 -  Amino Settop boxes (IPTV)
	 	 
	 	 - Knowledge on Supervision Controls SVN, Git., Code Collaborator
 	 	  
 \end{itemize}
 \hrulefill
 
 \section*{Working Experience}
  \subsection*{Role: Window Software Engineer}
  \begin{itemize}
  	\item  Company : Johnson Control Tyco Fire Panel
  	\item Period   : 12th Dec 2016 $-$ Current
  	\item Duties
  	
  	$-$Maintaining and debugging to reduce system bugs on the MXZ Consys Configuration Tools. 
  	
  	$-$As part of the NG Consys team to developed the new NG Consys Configuration Tools, Is also my duties to write new requirement (functional Item) for Tyco's Panels
  	
  	$-$Integration testing of the application to meet up with new requirements.
  \end{itemize}
  
  \subsection*{Role: Software Engineer}
  \begin{itemize}
  	\item  Company : Tripleplay-Services
  	\item Period   : 4th Apirl 2016 $-$  12th Auguest 2016
  	\item Duties
  	
  	   $-$Maintaining and debugging to reduce system bugs. 
  	   
  	   $-$Writing and implementing new application features.
  	   
  	   $-$Testing exists system software to meet up with requirements.
  \end{itemize}


  \subsection*{Role: Intern C$++/C\#$ Software Engineer}
  \begin{itemize}
  	\item  Company :  Iris Software London.
  	\item Period   : 4th August 2014 to 26th September 2014
  	\item Duties
  	
       $-$Debugging and reducing  existing system bugs.
       
       $-$Integrating new features into existing product.
       
       $-$ Implementing POC for new features.
  \end{itemize}
  
 \hrulefill
\section*{Education History}
\subsection*{$-$ West London University}
\subsubsection*{$-$ Computer Science [ 1st class(Hons.) ]}
\subsection*{Subject Includes}
\begin{itemize}
	\item  Grid Computing
	\item Distributing System
	\item Functional Programming
	\item Object Oriented Programming
	\item Database designed and Modelling.
	\item Middle-ware programming
	\item Databases and SQL
\end{itemize}


\subsection*{$-$ Auchi Polytechnic}
\subsubsection*{$-$ Computer Science[Upper credit 3.36] }
\subsection*{Subject Includes}
\begin{itemize}
	\item System Design \& Development
	\item  Research Methods
	\item Functional Programming
	\item Principles of Accounting I
	\item Descriptive Mathematics and Statistical Theory.
	\item Linear Programming
	\item Databases and SQL
\end{itemize}	
\hrulefill
\section*{Projects}
\textbf{Flight Management System}: A PHP/MYSQL application for flight booking management.

\textbf{Front-End Compiler}: A simple object oriented front-end compiler for academic purpose(POC).

\textbf{Ticket Management System}: A VB.Net application for managing cinema tickets (school assignment).

\textbf{Simple JavaScript 3D Engine}: A prove of concept to implement a JavaScript 3D OpenGL Rendering engine for graphical programming.

\textbf{ReactJS Live Media Player} React  live media player to play user local camera.



\subsection{Source Control}
\begin{itemize}
	\item $http://github.com/miljimo$ and
	\item  $  http://github.com/jimobama .$
\end{itemize} 
\hrulefill
\section{Hobbies}
Enjoy programming (artifects), table tennis, basket ball at leisure time.
\section*{References}
Will be provided on request.
\end{document}