\documentclass[11px]{article}

\usepackage[a4paper, total={7in, 9.3in},top=20mm,bottom=10mm]{geometry}


\begin{document}
	\begin{center}
	\section*{Obaro I. Johnson}
	Email: johnson.obaro@hotmail.com
	
    Phone: $+$44(0)7423004067
    \end{center}
    %Horizontal line
   \makebox[\linewidth]{\rule{\paperwidth}{0.1pt}}
	
	\subsection*{Profile}
	I study computer science at University of West London, UK, graduated 2015. I have advance software and computing skills set and also have previously worked in hotel and healthcare setups.I have gained customer services skill from my previous works experience,  also with 
	a drives to learn new skills and able to work  in a challenging environment.
	
\section*{Skills}
 \begin{itemize}
 	\item IT Skills, Customer Relationship
 	\item Problem Solving Skills.
 	\item Mathematical Knowledge,
 	\item Microsoft Office Suite(Excel, PowerPoint)
 	
 \end{itemize}
 \hrulefill
  \section*{Working Experience}
  
  \subsection*{Role: Receptionist}
  \begin{itemize}
  	\item  Company : Ehbo  Hotel, Nigeria
  	\item Period   : 17th Jan. 2009  -  12th Jan 2010
  	\item Duties
  	$-$ Booking  and reserving rooms for customer.
  	$-$ Reserving rooms , offices  and serving customer drinks in the bar.
  	
  \end{itemize}
  
  \subsection*{Role: Computer Teacher}
  \begin{itemize}
  	\item  Company : St. John's Primary \& School School.
  	\item Period   : 29th Jan. 2010  -  12th Sept, 2010.
  	\item Duties
  	$-$ Teachning computer related subject including maths.
  	$-$ Writing and producing end term results for pupils.
  	
  

  \subsection*{Role: Social Worker}
  \begin{itemize}
  	\item  Company : CareOut Look
  	\item Period   : 4th Jan. 2014  -  12th Jan 2015
  	\item Duties
  	   $-$Supporting both adult and children who are less privillages. 
  	
\end{itemize}

  \subsection*{Role: Intern C$++/C\#$ Software Engineer}
  \begin{itemize}
  	\item  Company :  Iris Software London.
  	\item Period   : 4th August 2014 – 26th September 2014
  	\item Duties
  	
       $-$Debugging and reducing  existing system bugs.
       
       $-$Implementing  new product features into exists one.
  \end{itemize}
  
 \hrulefill
\section*{Education History}
\subsection*{$-$ West London University}
\subsubsection*{$-$ Computer Science [ 1st class(hons.) ]}
\subsection*{Subject Includes}
\begin{itemize}
	\item  Grid Computing
	\item Distributing System
	\item Functional Programming
	\item Object Oriented Programming
	\item Database designed and Modelling.
	\item Middle-ware programming
	\item Databases and SQL
\end{itemize}


\subsection*{$-$ Auchi Polytechnic}
\subsubsection*{$-$ Computer Science[Upper credit 3.36] }
\subsection*{Subject Includes}
\begin{itemize}
	\item System Design \& Development
	\item  Research Methods
	\item Functional Programming
	\item Principles of Accounting I
	\item Descriptive Mathematics and Statistical Theory.
	\item Linear Programming
	\item Databases and SQL
\end{itemize}	
\hrulefill
.

\section{Hobbies}
Programming , playing table tennis, Football , Basket Ball  at leisure time.
\section*{References}
Will be provided on request.

\end{document}